Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-24 papers/BON_VHDL/paper.tex
added more in section 3

\lstdefinelanguage{Bon} {
  morekeywords={require,ensure,feature,old,and,o,Q'slew,end,Result,INTEGER},
  morekeywords={class,delta,invariant,inherit,deferred,effective,NONE,make},
  morecomment=[l]{--}, 
  morecomment=[s]{/*}{*/}, 
  morestring=[b]", 
 literate=,
  showstringspaces=false
}

@@

\subsection{Contracting}
\emph{Contracting} is the precise definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ). 
In VHDL-AMS \emph{simultaneous statement} represents analogue constraint of 
continuous-time waveform. In other words, simulator evaluates quantities such 
that the constraints specified by the simultaneous statements are satisfied. 
We admit that the constraint of waveform is nothing else than \emph{invariant}.
Another example of \emph{invariant} is conservation of energy law in which 
the summation of \arcoss quantities (\texttt{$\sum_{loop}$ across quatities =0}) 
around any closed path (loop) equals zero and the summation of through 
quantities (\texttt{$\sum_{node}$ through quatities =0}) at any node equals zero. 
Moreover, any predefined (implicite) attribute in VHDL 
has defined \emph{pre}/\emph{post condition} trought input/output 
parameters and theirs constraints. Furthermore any \emph{subtype} represents restricted
set of values from a base \emph{type}. The condition that determines which values are in the
\emph{subtype} may be \emph{contracted} by specifying characteristic predicate. 
For example, the \emph{subtype} \lstinlinenc|bit| of \lstinlinen|INTEGRER| may be defined as:\\
Therefore as an approach of best modelling practices, and as the notation 
based on contract design, BON is the obvious choice 
for the our simulator.
Throughout this paper we will try to make this clear.

>>>>

\lstdefinelanguage{Bon} {
  morekeywords={require,ensure,feature,old,and,o,Q'slew,end,Result, Void},
  morekeywords={class_chart,class,delta,invariant,inherit,deferred,effective,NONE,make},
  morekeywords={explanation,query,command,constraint},
  morecomment=[l]{--}, 
  morecomment=[s]{/*}{*/}, 
  morestring=[b]", 
 literate=,
  showstringspaces=false
}

@@

\subsection{Contracting}
\emph{Contracting} is the precise definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ). 
In VHDL-AMS \emph{simultaneous statement} represents analogue constraint of 
continuous-time waveform. In other words, analog kernel calculate quantities such 
that the constraints specified by the simultaneous statements are satisfied. 
We will agree that the constraint of waveform is nothing else than \emph{invariant}.
Another example of \emph{invariant} is conservation of energy law in which 
the summation of \arcoss quantities (\texttt{$\sum_{loop}$ across quatities =0}) 
around any loop equals zero and the summation of through 
quantities (\texttt{$\sum_{node}$ through quatities =0}) at any node equals zero. 
Moreover, any predefined (implicite) attribute in VHDL 
has defined pre/post condition trought input/output 
parameters and theirs constraints. Furthermore any subtype/subnature 
represents restricted set of values from a base type/nature. 
The condition that determines which values are in the subtype/subnature 
may be contracted by specifying characteristic predicate. 
For example, in typed $\lambda$ calculi, the subtype \lstinlinenc|bit| of 
positive integer may be defined as \texttt{bit:=$\lambda$ n:nat.n < 2}. 
The corresponding informal and formal BON transformation looks like:
\input{bitbon}
Therefore as an notition based on contract design, and as  methodology of 
best modelling practices, BON is the obvious choice for the our simulator.
Throughout this paper we will try to make this more clearly.
